%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Reposit Power Pty Ltd} % Organisation
    {Fyshwick, Australia} % Location
    {Oct 2023 - Present} % Date(s)
    {
      \cvsummary{Build and support Python services, Linux device agents, and telemetry workflows for energy systems, working across device behaviour, messaging paths, backend services, and operational tooling.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Extended energy-controller services for WiFi reconnect logic, telemetry reporting, status logging, and device monitoring across Linux-based field systems.}
        \item {Diagnosed production issues by breaking faults into device, messaging, backend, and infrastructure layers, then using logs, ping tests, interface checks, and Linux diagnostics to isolate root causes.}
        \item {Implemented and supported message-processing paths for telemetry and reconnect events across ZeroMQ and Kafka-based workflows, including schema-driven payload handling.}
        \item {Built repeatable engineering workflows with Docker, Jenkins, and Debian packaging for ARM builds, driver validation, and release preparation.}
        \item {Turned recurring operational issues into handover notes, dependency guides, and health checks that reduced repeat investigation and sped up recovery for the team.}
        \item {Worked across engineering and business teams to land repeatable fixes, clearer procedures, and lower operational friction in day-to-day operations.}
      \end{cvitems}
    }

  \cventry
    {Backend Developer} % Job title
    {4DATA IT} % Organisation
    {Queanbeyan, Australia} % Location
    {Jul 2023 - Oct 2023} % Date(s)
    {
      \cvsummary{Developed backend features and integrations for the ACTSmart Business Training platform, combining implementation work with deployment, testing, and release support.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Translated stakeholder requests and integration requirements into deliverable modules with clearer scope and less rework.}
        \item {Documented configuration, architecture, and end-to-end test paths so troubleshooting and release work could proceed with less guesswork.}
        \item {Used Docker and Docker Compose to make setup, recovery, and debugging more repeatable for the team.}
        \item {Supported integration delivery by linking code changes, environment setup, and release validation into a clearer handoff path for the project team.}
      \end{cvitems}
    }

    
  \cventry
    {Research Assistant} % Job title
    {QuantEcon} % Organisation
    {Canberra, Australia} % Location
    {Apr 2023 - Aug 2023} % Date(s)
    {
      \cvsummary{Built Python-based data and reporting workflows for research projects, supporting academic analysis in a university setting.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved data integrity and reduced manual cleanup by building reliable preparation workflows for research use.}
        \item {Maintained and extended databases for economic and financial time-series analysis, reducing manual reconciliation effort in reporting workflows.}
        \item {Translated technical findings into decision-ready summaries that improved communication between technical work and academic users.}
      \end{cvitems}
    }
  
  \cventry
    {Full Stack Developer \& Scrum Master} % Job title
    {Jemma} % Organisation
    {Canberra, Australia} % Location
    {Jul 2022 - May 2023} % Date(s)
    {
      \cvsummary{Contributed to product delivery across implementation, sprint coordination, and stakeholder communication in a client-facing software environment.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated competing work items across developers, stakeholders, and clients, helping the team prioritise requests and keep delivery aligned to deadlines.}
        \item {Planned and maintained project documentation throughout delivery, reducing ambiguity during handoffs and improving client communication.}
        \item {Managed Jira-based workflows to surface blockers and dependencies early, improving control across multiple technical tasks.}
      \end{cvitems}
    }

  \cventry
    {Product Manager, Commercial Products} % Job title
    {ByteDance} % Organisation
    {Beijing} % Location
    {Oct 2021 - Jan 2022} % Date(s)
    {
      \cvsummary{Improved internal product workflows and data visibility for commercial systems used by operations teams.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved CRM data access and visualization workflows, helping operations teams answer performance questions faster with less manual lookup.}
        \item {Worked directly with international stakeholders to convert business needs into technical specs and prototypes, reducing implementation rework.}
        \item {Delivered the Grant Cost field integration in CRM performance pages, removing cross-platform lookups and reducing manual retrieval effort by 20\%.}
      \end{cvitems}
    }

  \cventry
    {Product Operations, Commercial Products} % Job title
    {ByteDance} % Organisation
    {Beijing} % Location
    {Jul 2021 - Oct 2021} % Date(s)
    {
      \cvsummary{Supported internal tool adoption through Q\&A, testing, documentation, and user enablement for commercial product teams.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed online Q\&A channels and built FAQ content for CRM and performance tools, improving support consistency and surfacing recurring issues for product teams.}
        \item {Conducted user acceptance testing and monitored data quality, helping maintain service standards and catch issues before broader rollout.}
        \item {Created reference documentation, mini-courses, and recurring training sessions, reducing repeat support questions and helping users adopt new features more smoothly.}
      \end{cvitems}
    }

  \cventry
    {Operation and Maintenance Engineer} % Job title
    {TitanOS} % Organisation
    {WuHan} % Location
    {Nov 2019 - Jan 2020} % Date(s)
    {
      \cvsummary{Supported containerised service environments for runtime operations and platform maintenance.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed and maintained Docker-based services, reducing environment drift and lowering manual intervention during runtime recovery.}
        \item {Supported Kubernetes operations to reduce manual container management overhead and improve platform readiness.}
      \end{cvitems}
    }

\end{cventries}
